---
title: 'Christian Fishers Ethics Projects'
output: 
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    code_download: true
---

# Assignment 1
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
```

```{r libraries}
library(tidyverse)         # for graphing and data cleaning
theme_set(theme_minimal()) # Lisa's favorite theme
```

# Final Project Ideas 
A topic I'm interested in using for my final project is a crash reporting data set. This data set would consists of data collected from automobile crashes either in a specific state or city. 

I would find this data on Kaggle, data.gov, or specific transportation websites of a particular state. The data search for a good data set on automobile crashes shouldn't be hard to find since data is being collected each and every day on this particular issue. The cleaning process may be a hard step once I get to that point, due to manual data entries typically resulting in missing data. 

The challenges I foresee myself having is finding a complete data set with not an abundance of missing data, this issue can be solved by removing unimportant data, using place fillers, or inputting a mean or median value for numerical data. Another challenge I inticipate is now understanding the streets or locations an accident took place. For example, A wreck on interstate 7 in Texas, i wouldn't be familiar with, but a wreck on I-81 in Virginia I would be. So, if its not a a Virginia automobile data set I will need to do some additional research to understand the locations the crashes are taking place. 

# Portfolio Podcast
After listening to the Chapter 4: Building a Portfolio, 
A portfolio is essentially a collection of Data Analytically projects that I have completed throughout my Analytically career. A portfolio can be useful in many ways including a central point for easy to locate projects I have completed, showcase my analytically skills through codes and visualizations, become apart of a new analytical community, and provides another avenue for future employers to find and see my skills. 
